\include{header}


\newcommand{\papertext}[1]{#1}
\newcommand{\techreport}[1]{#1}

\newcommand{\alex}[1]{\noindent{\color{darkgreen}{Alexandra: #1}}}
\newcommand{\xlw}[1]{\noindent{\color{blue}{xl: #1}}}
\newcommand{\ewu}[1]{\noindent{\color{red}{EWu: #1}}}
\newcommand{\xxx}[1]{{\fontsize{13pt}{13pt}\selectfont\textcolor{red}{#1}}}
\newcommand{\codesize}{\fontsize{7}{8}}
\newcommand{\stitle}[1]{\vspace{0.5em}\noindent\textbf{#1}}
\newcommand{\calF}[0]{$\cal{F}$}

\newcommand{\ind}{\hspace{\algorithmicindent}}

% \newcommand{\deprecate}[1]{}
\newcommand{\deprecate}[1]{\noindent{\color{light-gray}{#1}}}

\newcommand{\prob}{{\sc Log-Corruption}\xspace}
\newcommand{\exact}{{\sc EXACTSOL}\xspace}
\newcommand{\qfix}{{\sc SingleQueryFix}\xspace}
\newcommand{\density}{{\sc DENSITY}\xspace}


\newcommand{\milpall}{\textsc{MILP-NAIVE}\xspace}
\newcommand{\milptuple}{\textsc{MILP-COMPL}\xspace}
\newcommand{\milptuplestopearly}{\textsc{MILP-COMPL-STOPEARLY}\xspace}
\newcommand{\milpadvtuple}{\textsc{MILP-ADV-TUPLE}\xspace}
\newcommand{\milpadvall}{\textsc{MILP-ADV-ALL}\xspace}
\newcommand{\heurstic}{\textsc{HEURISTIC}\xspace}

\pagenumbering{arabic}

%%Ensuring that equation labels remain normal size, even if we shrink the equation text
\makeatletter
\def\maketag@@@#1{\hbox{\m@th\normalfont\normalsize#1}}
\DeclareRobustCommand*\textsubscript[1]{%
          \@textsubscript{\selectfont#1}}
        \def\@textsubscript#1{%
          {\m@th\ensuremath{_{\mbox{\fontsize\sf@size\z@#1}}}}}
\makeatother

\newcommand{\sysname}{\textsc{QueryFix}}
\newcommand{\sys}{QFix\xspace}
\newcommand{\naive}{\sysname\textsubscript{basic}\xspace}
\newcommand{\tslice}{\sysname\textsubscript{ts}\xspace}
\newcommand{\qslice}{\sysname\textsubscript{qs}\xspace}
\newcommand{\aslice}{\sysname\textsubscript{as}\xspace}
\newcommand{\incremental}{\sysname\textsubscript{inc}\xspace}

% End of preamble. Here it comes the document.
\begin{document}

% for 
\title{{\sys}: Demonstrating error diagnosis in query histories}

\numberofauthors{3}
\author{
  \alignauthor Xiaolan Wang\\
    \affaddr{School of Computer Science}\\
    \affaddr{University of Massachusetts}\\
    \email{xlwang@cs.umass.edu}\\
  \alignauthor Alexandra Meliou\\
  \affaddr{School of Computer Science}\\
    \affaddr{University of Massachusetts}\\
    \email{ameli@cs.umass.edu}\\
  \alignauthor Eugene Wu\\
    \affaddr{Computer Science}\\
    \affaddr{Columbia University}\\
    \email{ewu@cs.columbia.edu}\\
}




{
\maketitle
}

\begin{abstract}

An increasing number of applications in all aspects of society rely on
data. Despite the long line of research in data cleaning and repairs,
data correctness has been an elusive goal. Errors in the data can be
extremely disruptive, and are detrimental to the effectiveness and
proper function of data-driven applications. Even when data is
cleaned, new errors can be introduced by applications and users who
interact with the data. Subsequent valid updates can obscure these
errors and propagate them through the dataset causing more
discrepancies. Any discovered errors tend to be corrected
superficially, on a case-by-case basis, further obscuring the true
underlying cause, and making detection of the remaining errors harder.

In this demo proposal, we outline the design of \sys, a {\it query-centric}
framework that derives explanations and repairs for discrepancies in 
relational data based on potential errors in the queries that operated on the data. 
This is a marked departure from traditional {\it data-centric} techniques that directly fix the data.
We then describe how users will use \sys in a demonstration scenario. 
Participants will be able to select from a number of 
transactional benchmarks, introduce errors into the queries that are executed,
and compare the fixes to the queries proposed by \sys as well as existing alternative algorithms
such as decision trees.

\end{abstract}

\input{content/01-introduction}
\input{content/02-arch}
\input{content/xx-problem}
\input{content/xx-demo}
%\input{content/xx-related}

\balance


{
% If you want to use smaller typesetting for the reference list,
% uncomment the following line:
%\small
%\bibliographystyle{acm-sigchi}
\bibliographystyle{abbrv}
\bibliography{main}
}

%\techreport{\input{content/appendix.tex}}






\end{document}
