%!TEX root = ../main.tex


\section{A MILP-based Solution}
\label{sec:sol}

The {\it Optimal Diagnosis} problem states that a log repair should resolve all complaints when re-executing the repaired log on the initial (possibly empty) database state.
The key challenge is that solutions must be able to handle data dependencies between queries in the log (e.g., $q_i$ reads what $q_j$ wrote).
Unfortunately, this challenge renders existing database techniques~\cite{Wu13,Chapman2009}, as well as machine learning-based approaches, infeasible because they are designed to ``repair'' individual non-nested \texttt{SELECT} queries.
Appendix~\ref{sec:heuristic} uses a decision tree-based approach to highlight why learning-based techniques perform poorly for even a single DML statement, and fail to work for more than one query.

To address these cross-query dependencies, we introduce a constraint-based approach to the {\it Optimal Diagnosis} problem.
To do so, it maps the problem into a mixed-integer linear programming (MILP) problem by linearizing and parameterizing the corrupted query log over the tuples in the database.
Briefly, a MILP problem involves assigning values to a set of undetermined variables such that they satisfy a set of linear equations and minimize an objective function---it is mixed because the variables may be integers or real numbers.

Our general strategy is to model each query as a linear equation that computes the output tuple values from the inputs and to transform the equation into a set of of linear constraints.   
In addition, the constant values in the queries are parameterized into a set of undetermined variables, while the database state before and after the query is encoded as constraints on the initial and final tuple values.
Finally, the objective function over the undetermined variables prefers assignments that minimize the amount that the queries change and the number of non-complaint tuples that are affected. 

The rest of this section will introduce the properties of MILP solvers, describe how to encode a single query and single tuple attribute, then extend the encoding procedure to the entire database and query log.
We finally define the objective function.
Subsequent sections introduce optimizations and variations of the problem.

\subsection{MILP Solvers}
\label{sec:MILP}

MILP problems are known to be NP-hard with respect to the number of constraints and undetermined variables, however numerous pruning and pre-processing optimizations and heuristics have made solvers very fast~\cite{quesada1992lp,stubbs1999branch,savelsbergh1994preprocessing,danna2005exploring,rothberg2007evolutionary,achterberg2009scip}.  
As a result, MILP solvers are both quite efficient and widely used in practice for applications such as trajectory planning~\cite{Ma2006, Richards02_JGCD, Kuwata2005a}, assembly and scheduling processes~\cite{Floudas2005, Sawik2011, Sawik2000}, and general decision support~\cite{Sabater2009, Milan2013}.
Modern solver performance is primarily sensitive to \textit{the number of constraints} and \textit{the number of undetermined variables} in the problem~\cite{atamturk2005integer,meindl2012analysis,gearhart2013comparison}. 
One of our key contributions in this paper is to use this observation to design a set of optimizations to dramatically reduce the size of the MILP problem---enough so that we can produce repairs for TPC-C workloads within one second.


\subsection{Encoding a Single Query}
\label{sec:linearize}

\if{0}
  We model a query $q_i$ as a conditional function $f_{q_i}(t)$ that takes as input a tuple $t$
  and returns its next state $t'$.  $f_{q_i}$ is applied to each 
  tuple $t \in \mathcal{D}_{i-1} \cup \{\bcancel{t}\}$ in the input relation along with a special
  non-existant tuple $\bcancel{t}$. \ewu{maybe fold this into the data model.}
  By treating the query as a function, we are able to encode its effects into a set
  of linear inequality constraints.  We call this process the linearization and 
  parameterization of a query.

  \begin{definition} [Conditional Function]
  \label{def:cond}
    The conditional function for query $q$ is:
    \[
      f_{q_i}(t)= 
      \begin{cases}
      f_{q_i.\mu} (t) ,& \text{if } f_{q_i.\sigma} (t)\\
      t,              & \text{otherwise}
      \end{cases}
  \]
  where the \textit{update function} $f_{q_i.\mu}$ models a set of \textit{update equation(s)};
  and the \textit{condition function} $f_{q_i.\sigma}$ models a set of \textit{logical expression(s)} in 
  disjunctive or conjunctive form.
  \end{definition} 



  Conditional functions can describe the common classes of update queries:
  \begin{enumerate}
  \item \texttt{UPDATE}: $f_{q_i.\mu}(t)$, $f_{q_i.\sigma}(t)$ model the \texttt{SET}
        and \texttt{WHERE} clauses.  For example, $f_{q_i.\mu}(<t.a, t.b>) = <t.a + 1, 2>$ and
        $f_{q_i.\sigma}(t) = (t.a > 20)$ corresponds to the query 
        \texttt{UPDATE D SET a = a + 1, b = 2 WHERE a > 20}.

  \item \texttt{INSERT}: $f_{q_i.\mu}(t)$ returns the inserted tuple, while 
        $f_{q_i.\sigma}(t) = (t = \bcancel{t})$ evaluates to true when it is executed over
        the special nonexistant tuple.

  \item \texttt{DELETE}: $f_{q_i.\mu}(t) = \bcancel{t}$ returns a nonexistant tuple whenever
        the predicate encoded in $f_{q_i.\sigma}(t)$ evaluates to true.
        For example, the query \texttt{DELETE FROM T WHERE a < 20} represents 
        $f_{q_i.\sigma}(t) = (t.a < 20)$.
        
  \end{enumerate}

  Finally, we parameterize $q_i$ by replacing all numeric constants in the
  conditional function with undetermined variables.   Consider the conditional
  function for \texttt{UPDATE} above: the constants $1$, $2$ in $f_{q_i.\mu}$
  as well as $20$ in $f_{q_i.\sigma}$ will be transformed into undetermined
  variables \texttt{v1, v2, v3} that are solved by the MILP solver.

\fi




MILP problems express constraints as a set of linear inequalities. Our
task is to derive such a mathematical representation for each query in
$\mathcal{Q}$. Starting with the functional representation of a
query (Section~\ref{sec:models}), we describe how each query type,
\texttt{UPDATE}, \texttt{INSERT}, and \texttt{DELETE}, can be
transformed into a set of linear constraints over a tuple $t$ and an
attribute value $A_j$.



\smallskip
\noindent
\texttt{UPDATE:}
Recall from Section~\ref{sec:models} that query $q_i$ can be modeled
as the combination of a modifier function $\mu_{q_i}(t)$ and
conditional function $\sigma_{q_i}(t)$. First, we introduce a binary
variable $x_{q_i, t}$ to indicate whether \newtext{query $q_i$ 
modifies the value of tuple $t$: 
\begin{align}
\label{eq:x}
x_{q_i, t} = x_{q_i, t}' \otimes \sigma_{q_i}(t)
\end{align}
Where $x_{q_i, t}'$ is a binary indicator that
reflects whether the tuple $t$ exists in the database
before executing $q_i$. When $x_{q_i, t}'$ is false, $x_{q_i, t}$
is guaranteed to be false, otherwise, the value of $x_{q_i, t}$ is dependent
on whether $t$ satisfy the condition function of $q_i$.
We will introduce the setting of $x_{q_i, t}'$ for \texttt{DELETE} queries.
}

%$t$ satisfies the
%conditional function of $q_i$: $x_{q_i, t}=1$ if
%$\sigma_{q_i}(t)=\texttt{true}$ and $x_{q_i, t}=0$ otherwise. In a
%slight abuse of notation:

%\newtext{\footnote{\newtext{To account for tuple deletions, the exact formula is actually more nuanced: $x_{q_i, t} =
%x'_{q_i, t} \otimes 0 + (1-x'_{q_i, t}) \otimes \sigma_{q_i}(t)$, where
%$x'_{q_i, t}= (t.A_j = M^-) \wedge (t.A_j^* = M^-)$, and $M^-$ is a ``ghost'' value assigned to attributes of deleted tuples (see \texttt{DELETE}).}}}

Next, we introduce real-valued variables for the attributes of $t$.
We express the updated value
of an attribute using semi-modules, borrowing from the models of
provenance for aggregate operations~\cite{Amsterdamer2011}. A
semi-module consists of a commutative semi-ring, whose elements are
scalars, a commutative monoid whose elements are vectors, and a
multiplication-by-scalars operation that takes a scalar $x$ and a
vector $u$ and returns a vector $x \otimes u$. A similar formalism has
been used in literature to model hypothetical data
updates~\cite{tiresias}.

Given a query $q_i$ and tuple $t$, we express the value of attribute $A_j$ in the updated tuple $t'$ as follows:
\begin{align}
\label{eq:linearization}
t'.A_j = x_{q_i, t}\otimes \mu_{q_i}(t).A_j + (1-x_{q_i, t})\otimes t.A_j 
\end{align} 
\looseness -1
In this expression, the $\otimes$ operation corresponds to regular
multiplication, but we maintain the $\otimes$ notation to indicate
that it is a semi-module multiplication by scalars. This expression
models the action of the update: If $t$ satisfies the conditional
function ($x_{q_i, t}=1$), then $t'.A_j$ takes the value
$\mu_{q_i}(t).A_j$; if $t$ does not satisfy the conditional function
($x_{q_i, t}=0$), then $t'.A_j$ takes the value $t.A_j$.
In our running example, the rate value of a tuple $t$ after query $q_1$ would be expressed as:
$t'.owed = x_{q_1, t}\otimes (t.income*0.3) + (1-x_{q_1, t})\otimes t.owed$.
Equation~\eqref{eq:linearization} does not yet provide a linear
representation of the corresponding constraint, as it contains
multiplication of variables. To linearize this expression, we adapt a
method from~\cite{tiresias}: We introduce two variables $u.A_j$ and
$v.A_j$ to represent the two terms of
Equation~\eqref{eq:linearization}: $u.A_j=x_{q_i, t}\otimes
\mu_{q_i}(t.A_j)$ and $v.A_j=(1-x_{q_i, t})\otimes t.A_j$. Assuming a
number $M$ is a large enough value~\cite{bazaraa2011linear} that is outside of the domain of $t.A_j$, we get the
following constraints:
\begin{align}
\label{eq:uv}
u.A_j &\!\leq\! \mu_{q_i}(t).A_j   &v.A_j &\!\leq\! t.A_j &\nonumber\\
u.A_j &\!\leq\! x_{q_i, t}M        &v.A_j &\!\leq\! (1\!-\!x_{q_i, t})M &\\
u.A_j &\!\geq\! \mu_{q_i}(t).A_j \!-\! (1\!-\! x_{q_i, t})M \phantom{i} 
&v.A_j &\!\geq\! t.A_j \!-\! x_{q_i, t}M &\nonumber
\end{align}
The set of conditions on $u.A_j$ ensure that $u.A_j = \mu_{q_i}(t).A_j$ if $x_{q_i, t}=1$, and $0$ otherwise. Similarly, 
the conditions on $v.A_j$ ensure that $v.A_j = t.A_j$ if $x_{q_i, t}=0$, and $0$ otherwise.  
Now, Equation~\eqref{eq:linearization} becomes linear:
\begin{align}
\label{eq:tnew}
t.A_j' = u.A_j + v.A_j
\end{align}

\noindent\texttt{INSERT:}\looseness -1
An insert query adds a new tuple $t_{new}$ to the database.  If the query were 
corrupted, then the inserted values need repair. We use a binary variable $x$ to model whether the query is correct.  Each attribute of the newly inserted tuple ($t'.A_j$) may take one of two values: the value specified by the insertion query ($t_{new}.A_j$) if the query is correct ($x=1$), or an undetermined value ($v.A_j$) if the query is incorrect ($x=0$).  Thus, similar with Equation~\eqref{eq:linearization}, we write:
\begin{eqnarray}
\label{eq:insert}
t'.A_j = x \otimes t_{new}.A_j + (1-x) \otimes v.A_j 
\end{eqnarray}


\smallskip
\noindent
\texttt{DELETE:}
A delete query removes a set of tuples from the database.  
Since the MILP problem doesn't have a way to express a non-existent value,
we encode a deleted tuple by setting its attributes to a
\emph{``ghost''} value, $M^-$, outside of the attribute domain. Since $M^-$ is
outside of the attribute domain, any subsequent conditional functions will
evaluate to false, so subsequent queries do not affect ghost tuples. There are
nuances to how $M^-$ is set. It needs to be sufficiently large, for the MILP
problem to prioritize a modification to the \texttt{WHERE} clause of the
\texttt{DELETE} query ($\sigma_{q_i}(t) = 0/1$), compared to a modification of
the \texttt{SET} clause of an \texttt{UPDATE} query to the ghost value
($\mu_{q_i}(t.A_j) = M^-$). However, it should be $M^- \leq M $ to ensure the
constraints remain feasible (Equation~\ref{eq:uv}). These considerations
ensure that the ghost assignment will not affect subsequent queries.
% So the $M^-$ assignment will not have an effect on subsequent queries encoded in the MILP problem:
%
% \xlw{Note that although the subsequent condition functions may be true initially, but any solutions having such positive conditions will have an associated objective-function value that is exceedingly large. Thus the MILP solver will always assign false to the subsequent condition functions.} 
\newtext{
\begin{eqnarray}
\label{eq:delete}
t'.A_j &=& x_{q_i, t} \otimes M^- + (1-x_{q_i, t}) \otimes t.A_j 
\end{eqnarray}
Where we use Equation~\ref{eq:x} for variable $x_{q_i, t}$. 
In addition, we set the binary variable $x_{q_i, t}'$ to true (in Equation~\ref{eq:x})
if it is correctly deleted from the database.
\begin{eqnarray}
\label{eq:delete_x}
x_{q_i, t}' &=& (t.A_j = M^-) \wedge (t^*.A_j = M^-)
\end{eqnarray}}
This expression is further linearized using the same method as Equation~\eqref{eq:uv}.

\smallskip
\noindent
\textbf{Putting it all together.}
The constraints defined in Equations \eqref{eq:x}--\eqref{eq:delete}
form the main structure of the MILP problem for a single attribute
$A_j$ of a single tuple $t$. To linearize a query $q_i$ one needs to
apply this procedure to all attributes and tuples. This process is
denoted as $Linearize(q, t)$ in Algorithm~\ref{alg:basic}. Our MILP
formulation includes three types of variables: the binary variables
$x_{q_i, t}$, the real-valued attribute values (e.g., $u.A_j$), and
the real-valued constants in $\mu_{q_i}$ and $\sigma_{q_i}$. All these
variables are undetermined and need to be assigned values by a MILP
solver.
  

Next, we extend this encoding to the entire query log,
and incorporate an objective function encouraging solutions
that minimize the overall changes to the query log.







\subsection{Encoding and Repairing the Query Log}
\label{sec:milp}

We proceed to describe the procedure (Algorithm~\ref{alg:basic}) that encodes 
the full query log into a MILP problem, and solves the MILP problem to derive $\mathcal{Q}^*$.
The algorithm takes as input the query log $\mathcal{Q}$, 
the initial and final (dirty) database states 
$\mathcal{D}_{0, n}$, and the complaint set $\mathcal{C}$, and outputs a fixed query 
log $\mathcal{Q}^*$.  

\looseness -1
We first call \textit{Linearize} on each tuple in $\mathcal{D}_0$ and
each query in $\mathcal{Q}$, and add the result to a set of
constraints \textit{milp\_cons}. The function \textit{AssignVals} adds
constraints to set the values of the inputs to $q_0$ and the outputs
of $q_n$ to their respective values in $\mathcal{D}_0$ and
$\mathcal{T}_\mathcal{C}(\mathcal{D}_n)$. Additional constraints
account for the fact that the output of query $q_i$ is the input of
$q_{i+1}$ (\textit{ConnectQueries}). This function simply equates $t'$
from the linearized result for $q_i$ to the $t$ input for the
linearized result of $q_{i+1}$.

Finally, \emph{EncodeObjective} augments the program with an objective
function that models the distance function between the original query
log and the log repair ($d(\mathcal{Q},\mathcal{Q}^*)$). In the
following section we describe our model for the distance function,
though other models are also possible. Once the MILP solver returns a
variable assignment, \textit{ConvertQLog} updates the constants in the
query log based on this assignment, and constructs the fixed query log
$\mathcal{Q}^*$.





\begin{algorithm}[t]
\caption{$Basic:$ The MILP-based approach.}
\label{alg:basic}
\scriptsize
\begin{algorithmic}[1]
\REQUIRE {$\mathcal{Q}, D_0, D_n, \mathcal{C}$}
\STATE $milp\_cons \leftarrow \emptyset$
\FOR {each $t$ in $R$}
\FOR {each $q$ in $\mathcal{Q}$}
\STATE $milp\_cons \leftarrow milp\_cons \cup Linearize(q, t)$
\ENDFOR
\STATE $milp\_cons \leftarrow milp\_cons \cup AssignVals(D_0.t, D_n.t, \mathcal{C})$
\FOR {each $i$ in $\{0,\ldots,N-1\}$}
\STATE $milp\_cons \leftarrow milp\_cons \cup ConnectQueries(q_i, q_{i+1})$
\ENDFOR
\ENDFOR 
\STATE $milp\_obj \leftarrow EncodeObjective(milp\_cons, \mathcal{Q})$
\STATE $solved\_vals \leftarrow MILPSolver(milp\_cons, milp\_obj)$
\STATE $\mathcal{Q}^* \leftarrow ConvertQLog(Q, solved\_vals)$
\STATE Return $\mathcal{Q}^*$
\end{algorithmic}
\end{algorithm}



















